### 2015-06-08 LOI/inc2.tex
A pass on the entire LOI.
Commented out some text that look repeated.

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards.  Our goal in this project is
to address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL,
Rutgers), file system (SNL, UCSC) and storage (UCSC), and connect and
coordinate these key storage components in a seamless fashion.

@@

  \setlength{\parindent}{0.5cm}
  Our objective here is to reduce the time to knowledge, not just for a single
application or workflow, but for the entire workload in the system. This is
an end-to-end system wide metric relevant to the scientific discovery
process. We will explore beyond the traditional I/O pattern of
checkpoint/restart, and will address the challenges posed by other essential
data access patterns in the knowledge gathering process.  Through a deeper
insight into the scientific process we will encode and utilize accuracy and
errors as optimization parameters.  
Finally, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically  between the user intentions and
the available system resources. Our overall goal is to ensure that optimizations can be made across
1) a single application, 2) an ensemble of applications, and 3) the entire suite of applications which are running on the system.

@@

Our overall technical approach is based on an application-aware runtime
realization of tradeoffs in data representation, data placement and data
access. We will allow users plug-in their knowledge 
about the data, represented not as bytes but as motifs, allowing the I/O and 
storage system to understand user
intentions, the relationships between data objects, and also data access
and transport patterns. This will facilitate efficient mapping of data from
user space onto various storage tiers, and application-guided
data reductions.

@@

Incorporating awareness of the data content and user intent  into
our decision making and data management process is integral to our approach. For example, 
we will offer a coarse grained, quick overview of a data set with progressively more detail in 
areas of interest such as those containing features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve. By defining mechanisms for applications to provide this 
knowledge and incorporating its awareness into our middleware  and storage allow
it will be able to selectively store data at different  levels, and allow a user to select what data to retrieve by specifying both an acceptable  timeframe and accuracy.

@@

The I/O and storage system prototype will enable

@@

different portions of a single dataset--even a single variable at differnt

@@

support the metadata and plug-ins reuired to support this sort of data storage

@@

notion of a time and data quality for requested data. The storage system,
through the knowledge of both the data quality stored in differeht storage

@@

tiers, the user can manage the tradeoff between data precision and time to
retrieve. This storage system support will be managed through middleware

@@

must also support plug-ins to potentially decompress or expand data to the

@@

simulation run purpose may have changed, we are focused on scalability where
subsequent runs are larger as the simulation prepares for a capability run.  By

@@

how to pull and store data sets. In some cases, a full fidelity will be pulled

@@

versions of the same data will be leveraged to offer eviction and migration. The main challenge of this approach is to keep in mind the intentional placement

@@

A key challenge in this project is defining and maintaining the metadata
connecting different object quality and utility levels, and using this metadata 
to most appropriately manage the placement and access of data object based on 
user/application intent/constraints and storage system state.
%The new user APIs required to interact with this rich metadata system will
%drive effective use of the entire middleware and storage stack.
Our research efforts will be heavily focused on the need to, in a
coordinated manner, adapt data and metadata retention policies to the
dynamic resource balancing that will need to take place between the
application, OS/R, and hardware.

The success of this project will provide insights into how to build
autonomic middleware and storage layers which can interact well with each
other, and take user-provided hints.  This will be managed against the needs of
individual simulations as well as what's happening on the entire system. This
will reduce the time to knowledge by allowing user and system knowledge into
the SSIO software layers.

>>>>

\underline{\textbf{Objectives:}} Exascale scientific discovery will be
severely bottlenecked without sufficient new research into managing and
storing the large amounts of data that will be produced during the
simulation, and analyzed for months afterwards.  Our goal in this project is
to address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes. To that end, we will build on the
capabilities offered by ADIOS and DataSpaces that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL,
Rutgers), file system (SNL, UCSC) and storage (UCSC), and connects and
coordinates these key storage components in a seamless fashion.

@@

 %% Manish: Commented this since it seems to be replicated below.  
%  Our objective here is to reduce the time to knowledge, not just for a single
%application or workflow, but for the entire workload in the system. This is
%an end-to-end system wide metric relevant to the scientific discovery
%process. We will explore beyond the traditional I/O pattern of
%checkpoint/restart, and will address the challenges posed by other essential
%data access patterns in the knowledge gathering process.  Through a deeper
%insight into the scientific process we will encode and utilize accuracy and
%errors as optimization parameters.  
%Finally, we will take the knowledge from the storage system to provide vital feedback to the middleware 
%so that the best possible decisions can be autonomically  between the user intentions and
%the available system resources. Our overall goal is to ensure that optimizations can be made across
%1) a single application, 2) an ensemble of applications, and 3) the entire suite of applications which are running on the system.

@@

Our overall technical approach is based on an application-aware runtime
realization of tradeoffs in data representation, data placement and data
access. We will allow users to plug-in their knowledge 
about the data, represented not as bytes but as motifs, allowing the I/O and 
storage system to understand user
intentions, the relationships between data objects, and also data access
and transport patterns. This will facilitate efficient mapping of data from
user space onto various storage tiers, and application-guided
data reductions/transformations.

@@

Incorporating awareness of the data content and user intent  into
our decision making and data management process is integral to our approach. For example, 
we will offer a coarse grained, quick overview of a data set with progressively more detail in 
areas of interest such as those containing features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve. By defining mechanisms for applications to provide this 
knowledge and incorporating its awareness into the middleware and storage,
we will be able to selectively store data at different levels, and allow a user to select 
not only what data to retrieve but also specify an acceptable timeframe and accuracy.

@@

Our proposed I/O and storage system prototype will enable

@@

different portions of a single dataset, even a single variable, at different

@@

support the metadata and plug-ins required to support this data storage

@@

notion of time and data quality for requested data. The storage system,
through knowledge of both the data quality stored in different storage

@@

tiers, can manage (with the user in the loop) the tradeoff between data precision and time to
retrieve. This storage system support will be executed and managed through our middleware, 

@@

must also support plug-ins, for example, to potentially decompress or expand data to the

@@

simulation details may have changed, we are focused on scalability where
subsequent runs are larger in scale as the simulation prepares for a capability run.  By

@@

how to pull and store data sets. In some cases, a full fidelity dataset may be pulled

@@

versions of the same data will be leveraged to guide data eviction and migration. 
The main challenge of this approach is to be aware of intentional placement

@@

A key challenge in this project is defining and maintaining the metadata
connecting different object quality and utility levels, and using this metadata 
to most appropriately manage the placement and access of data object based on 
user/application intent/constraints and storage system state.
%The new user APIs required to interact with this rich metadata system will
%drive effective use of the entire middleware and storage stack.
Our research efforts will be heavily focused on the need to, in a
coordinated manner, adapt data and metadata retention policies according to the 
dynamic resource balancing that will need to take place between the
application, OS/R, and hardware.

The success of this project will provide insights into how to build extreme scale
autonomic middleware and storage layers that can interact effectively with each
other, and bring the user in the loop through user-provided hints, allowing user 
and system knowledge to be incorporated into the SSIO software layers.
Storage resources will be managed against the needs of individual simulations 
as well as what's happening on the entire system. The impact of such a solution 
will be a significant reduction in the time to knowledge, and the overall increase in 
the effectiveness and utility of exascale simulations.
